\bf\mftitle

### 2011-03-02 doc/jInfer/tutorials/doc_tutorial.tex
Documentation: Tutorials: changing titles.
tutorial OK

\def\mftitle{jInfer Tutorial}
\def\mfauthor{Michal Klempa, Mário Mikula, Robert Smetana, Michal Švirec, Matej Vitásek}
\def\mfadvisor{RNDr. Irena Mlýnková, Ph.D., Martin Nečaský, Ph.D.}
\def\mfplacedate{Praha, 2011}
\title{\bf\mftitle}
\author{\mfauthor \\ Advisors: \mfadvisor}
\date{\mfplacedate}

@@

        \par 
          Note: we use the term \textbf{inference} for the act of creation of schema throughout this and other jInfer documents.

@@

\begin{enumerate}
  \item Go to https://sourceforge.net/projects/jinfer/files/.
  \item Download the latest jInfer binaries (jInfer-X.Y-bin.zip).
  \item Unpack the ZIP, you'll get a few NBM files.
  \item Start NetBeans, open \textit{Tools} > \textit{Plugins} from the main menu.
  \item Switch to \textit{Downloaded} tab.
  \item Click \textit{Add Plugins...}.
  \item Select all the unpacked NBM files.
  \item Click \textit{Install} and follow the instructions.
  \item Restart NetBeans.
  \end{enumerate}
\subsection*{Basic Inference}
\par 
  This section assumes you have NetBeans and jInfer installed. After the first run, a jInfer Welcome window will appear, guiding you through basically the same steps that will be covered here. You might want to follow them instead.

>>>>

\def\mftitle{jInfer User Tutorial}
\def\mfauthor{Michal Klempa, Mário Mikula, Robert Smetana, Michal Švirec, Matej Vitásek}
\def\mfadvisor{RNDr. Irena Mlýnková, Ph.D., Martin Nečaský, Ph.D.}
\def\mfplacedate{Praha, 2011}
\title{\bf\mftitle}
\author{\mfauthor \\ Advisors: \mfadvisor}
\date{\mfplacedate}

@@

        \par 
          \emph{Note: we use the term \textbf{inference} for the act of creation of schema throughout this and other jInfer documents.}

@@

\begin{enumerate}
  \item Go to \url{https://sourceforge.net/projects/jinfer/files/}.
  \item Download the latest jInfer binaries (jInfer-X.Y-bin.zip).
  \item Unpack the ZIP, you'll get a few NBM files.
  \item Start NetBeans, open \textit{Tools} > \textit{Plugins} from the main menu.
  \item Switch to \textit{Downloaded} tab.
  \item Click \textit{Add Plugins...}.
  \item Select all the unpacked NBM files.
  \item Click \textit{Install} and follow the instructions.
  \item Restart NetBeans.
  \end{enumerate}
\subsection*{Basic Inference}
\par 
  This section assumes you have NetBeans and jInfer installed. After the first run, a jInfer Welcome window will appear, guiding you through basically the same steps that will be covered here. You might want to follow them instead.
